---
title: "AirBNB Data Analysis"
author: "Tim Harrold, Madison brown, Yifei Hao"
date: "3/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)

```

## Setting up the project

First, get our data from:

http://insideairbnb.com/get-the-data.html


To create these two files, right click the files listings.csv.gz and reviews.csv.gz separately, and click "extract here" or "extract to -> listings.csv", just like we extract the .zip files in class

Before committing and pushing, go to github desktop after you have the data files. Where it lists each file with a checkbox, right click the data files "listings.csv,reviews.csv,listings.csv.gz" and click:     
"ignore all .csv files(add to .gitignore)", then     
"ignore all .gz files(add to .gitignore)". 

If the data files are not removed from the list, right click them again and click "Ignore File(add to .gitignore). This will make it so you don't submit large data to the cloud. Github will not accept these large files(even the compressed ones) because of the size of our data.

```{r setup}


listings <- read.csv('listings.csv');
reviews <- read.csv('reviews.csv');

tibble(listings)
tibble(reviews)



```

## Make some graphs!


```{r plots, echo=FALSE}



```

